coauthor_comments

### 2021-03-14 doc/manuscript/coauthor_feedback/2021_02/coauthor feedback.Rmd
updated references
(many changed when I updated my computer)
finished BG comments, (re)moved word file

@@

(Bianca's comments are in the file she sent, but alongside her own highlights. She reccommends just looking at the summary here.)

@@

@@

@@

>>>>

**updated in main manuscript and sites table (needs to be re-knit)**

@@

(Bianca's comments are in the file she sent, but alongside her own highlights. She recommends just looking at the summary here.)

@@

**This is one of three suggestions to split, which we're not doing, but hopefully the changes will make the message cleaarer.**

@@

**noted (but not yet sure what I'll end up doing).**

@@

**Removed the part suggested.**
